BMAC data analysis
========================================================

Uses data from Britain's Most Admired Companies (http://www.managementtoday.co.uk/go/bmac/).

```{r setup, cache=FALSE, include=FALSE}
opts_chunk$set(cache=TRUE)
```

```{r datasetup, echo=FALSE}
setwd("c:/documents and settings/dbarron/my documents/reputation/BMAC")
library(plyr)
library(ggplot2)
library(reshape)
library(scales)
library(RColorBrewer)
library(car)

bmac2011 <- read.csv("bmac2011.csv")
bmac2010 <- read.csv("bmac2010.csv")
bmac2009 <- read.csv("bmac2009.csv")
ix <- order(bmac2009$Industry,bmac2009$Company)
bmac2009 <- bmac2009[ix,]
ix <- order(bmac2010$Industry,bmac2010$Company)
bmac2010 <- bmac2010[ix,]
ix <- order(bmac2011$Industry,bmac2011$X)
bmac2011 <- bmac2011[ix,]
```


Dimensions
-------------------------------------
1. Quality of management (QMan)
2. Financial soundness (FS)
3. Quality of goods or services (QGS)
4. Ability to Attract, Develop and Retain Top Talent
5. Value as a long-term investment (VLTI)
6. Capacity to innovate (CI)
7. Quality of marketing (QMar)
8. Community and Environmental Responsibility (CER)
9. Use of corporate assets (UCA)

# 2009
## Descriptive statistics


```{r data2009}
cols <- c(4,6,8,10,12,14,16,18,20)
tot.col <- 22
ind.col <- 2
comp.col <- 3
inds2009 <- levels(bmac2009[,ind.col])
dta <- bmac2009[,c(ind.col,comp.col,cols)]
```

```{r descstats2009, warning=FALSE}
(means2009 <- ddply(dta,.(Industry), function(x) colMeans(x[,-(1:2)])))
(sds2009 <- ddply(dta,.(Industry), function(x) sapply(x[,-(1:2)],sd)))
means2009.m <- melt(means2009)
means2009.m <- ddply(means2009.m, .(variable), transform, rescale = rescale(value))
(p <- ggplot(means2009.m, aes(variable, Industry)) + geom_tile(aes(fill = rescale), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue"))
```

```{r radar2009}
ind2009 <- dlply(dta,.(Industry))
for (i in 1:25){
  x.m <- melt(ind2009[[i]],"Company",3:11)
  print(ggplot(x.m,aes(variable,Company)) + geom_tile(aes(fill=value),colour='white') + 
    scale_fill_gradient(low='white',high='steelblue') + ggtitle(inds2009[i]))
}

```

## Principal components
```{r pc2009}
pc2009 <- prcomp(bmac2009[,cols])
summary(pc2009)
pc2009$sdev^2
```
```{r pcind2009}
pcind2009 <- ddply(dta,.(Industry), function(x) {
  pctmp <- prcomp(x[,-c(1,2)])
  print(summary(pctmp))
#  screeplot(pctmp)
  })
```


# 2010

```{r data2010}
cols <- c(6,8,10,12,14,16,18,20,22)
tot.col <- 4
ind.col <- 3
comp.col <- 2

inds2010 <- levels(bmac2010[,ind.col])
dta2010 <- bmac2010[,c(ind.col,comp.col,cols)]
```
```{r descstats2010, warning=FALSE}
(means2010 <- ddply(dta2010,.(Industry), function(x) colMeans(x[,-(1:2)])))
(sds2010 <- ddply(dta2010,.(Industry), function(x) sapply(x[,-(1:2)],sd)))
means2010.m <- melt(means2010)
means2010.m <- ddply(means2010.m, .(variable), transform, rescale = rescale(value))
(p <- ggplot(means2010.m, aes(variable, Industry)) + geom_tile(aes(fill = rescale), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue"))
```


```{r radar2010}
ind2010 <- dlply(dta,.(Industry))
for (i in 1:25){
  x.m <- melt(ind2010[[i]],"Company",3:11)
  print(ggplot(x.m,aes(variable,Company)) + geom_tile(aes(fill=value),colour='white') + 
    scale_fill_gradient(low='white',high='steelblue') + ggtitle(inds2010[i]))
}
```

# 2011

```{r data2011}
cols <- c(2,4,6,8,10,12,14,16,18)
tot.col <- 20
ind.col <- 22
comp.col <- 1

inds2011 <- levels(bmac2011[,ind.col])
dta2011 <- bmac2011[,c(ind.col,comp.col,cols)]
```

```{r descstats2011, warning=FALSE}
(means2011 <- ddply(dta2011,.(Industry), function(x) colMeans(x[,-(1:2)])))
(sds2011 <- ddply(dta2011,.(Industry), function(x) sapply(x[,-(1:2)],sd)))
means2011.m <- melt(means2011)
means2011.m <- ddply(means2011.m, .(variable), transform, rescale = rescale(value))
(p <- ggplot(means2011.m, aes(variable, Industry)) + geom_tile(aes(fill = rescale), colour = "white") + scale_fill_gradient(low = "white", high = "steelblue"))
```


```{r radar2011}
ind2011 <- dlply(dta,.(Industry))
for (i in 1:25){
  x.m <- melt(ind2011[[i]],"Company",3:11)
  print(ggplot(x.m,aes(variable,Company)) + geom_tile(aes(fill=value),colour='white') + 
    scale_fill_gradient(low='white',high='steelblue') + ggtitle(inds2010[i]))
}
```
